MSF_Groupwork-NBA_shotlog

### 2016-10-09 MSFGroupwork-NBAHotHand.Rmd
calculate top 5 players with most 2 points and 3 points

###Introduction
I   What is your theme or research question?
a. Hot Hand Theory  
b. Defender Proximity Analysis (Reza)
c. Shot Clock Pressure  
d. Close Game Effect - Small Margin affecting the scoring rate  
e. Home Advantage (Alex is working in this point)  
f. Fatigue Effect (Quarter Heat Rate)  
g. Shooting Percentage  
h. Fatigue Effect (Number of Rest Day)  
i.

@@

#set the value to numeric
df[, "SHOT_RESULT"] <- as.numeric(df[, "SHOT_RESULT"])
df[, "PTS_TYPE"] <- as.integer(df[, "PTS_TYPE"])
df[, "CLOSE_DEF_DIS"] <- as.numeric(df[, "CLOSE_DEF_DIST"])

@@

#calculate correlation between defender distance and points made (2 or 3 points)
cor(df[, "PTS_TYPE"], df[, "CLOSE_DEF_DIS"])

#plot the diagram
library(ggplot2)
ggplot(data = df, aes(x = PTS_TYPE, y = CLOSE_DEF_DIST, group = PTS_TYPE)) + geom_boxplot() + stat_summary(fun.y = mean, geom = "point", shape = 5, size = 1) +ggtitle("Points Scored based on Distance from Defender")
```

>>>>

###Introduction
I   What is your theme or research question?
a. Hot Hand Theory  
b. Defender Proximity Analysis (Reza)
c. Shot Clock Pressure  (Alex)
d. Close Game Effect - Small Margin affecting the scoring rate  
e. Home Advantage (Alex is working in this point)  
f. Fatigue Effect (Quarter Heat Rate)  
g. Shooting Percentage (James)
h. Fatigue Effect (Number of Rest Day)  
i.

@@

#set the value to numeric or integer accordingly
df[, "SHOT_RESULT"] <- as.numeric(df[, "SHOT_RESULT"])
df[, "PTS_TYPE"] <- as.integer(df[, "PTS_TYPE"])
df[, "CLOSE_DEF_DIS"] <- as.numeric(df[, "CLOSE_DEF_DIST"])

#select data with only scored result
#Point type (2 or 3 points) and distance
point_type <- c()
distance <- c()
for (z in 1:nrow(df)){
  if(df[z, "SHOT_RESULT"] == 1 & df[z, "PTS_TYPE"] >= 1){
    point_type <- c(point_type, df[z, "PTS_TYPE"])
    distance <- c(distance, df[z, "CLOSE_DEF_DIST"])
  }
}

#combine point type and distance
valid_distance = data.frame(point_type, distance)

#calculate correlation between defender distance and points made (2 or 3 points)
cor(point_type, distance)

#plot the diagram for this correlation
library(ggplot2)
ggplot(data = valid_distance, aes(x = point_type, y = distance, group = point_type)) + 
  geom_boxplot() + stat_summary(fun.y = mean, geom = "point", shape = 5, size = 1) + 
  ggtitle("Points Scored based on Distance from Defender")

@@

#--------------------------------------------------------------------------------#

#further analysis
#select distance data from 2 points shot scored and the players who scored it
distance2 <- c()
players2 <- c()
for (z in 1:nrow(df)){
  if(df[z, "SHOT_RESULT"] == 1 & df[z, "PTS_TYPE"] == 2){
    distance2 <- c(distance2, df[z, "CLOSE_DEF_DIST"])
    players2 <- c(players2, as.character(df[z, "player_name"]))
  }
}

#combine 2 point players and defender distance
player2point <- data.frame(players2, distance2)
summary(player2point)

#count players who scored 2 points
counter <- as.data.frame(table(players2))

#count 5 top players
top5Players2 <- counter[rev(order(counter$Freq)), "players2"][1:5]
top5Counter <- counter[rev(order(counter$Freq)), "Freq"][1:5]

top5_2points <- data.frame(top5players2, top5Counter)

#plot the graph
library(ggplot2)
ggplot(data = top5_2points, aes(x = top5Players2)) + geom_bar(aes(x = top5players2, y = top5Counter), stat = "identity")

#----------------------------------------------------------------#

#select distance data from 3 points shot scored and the players who scored it
distance3 <- c()
players3 <- c()
for (z in 1:nrow(df)){
  if(df[z, "SHOT_RESULT"] == 1 & df[z, "PTS_TYPE"] == 3){
    distance3 <- c(distance3, df[z, "CLOSE_DEF_DIST"])
    players3 <- c(players3, as.character(df[z, "player_name"]))
  }
}

#combine 3 point players and defender distance
player3point <- data.frame(players3, distance3)
summary(player3point)

#count players who scored 3 points
counter3 <- as.data.frame(table(players3))

#count 5 top players
top5Players3 <- counter3[rev(order(counter3$Freq)), "players3"][1:5]
top5Counter3 <- counter3[rev(order(counter3$Freq)), "Freq"][1:5]

top5_3points <- data.frame(top5Players3, top5Counter3)

#plot the graph
library(ggplot2)
ggplot(data = top5_3points, aes(x = top5Players3)) + geom_bar(aes(x = top5Players3, y = top5Counter3), stat = "identity")
